\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage[style=apa]{biblatex}
\usepackage[hidelinks]{hyperref}
\usepackage{booktabs}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{hyperref}
\geometry{a4paper, margin=1in}
\addbibresource{references.bib}

% \title{}
\author{Your Name}
\date{Date of submission: \today}
\renewcommand{\arraystretch}{1.3}


% -------------------------------------------------------------------------------------------
\begin{document}

\include{titlepage.tex}
\pagebreak

\begin{abstract}
Your abstract goes here.
\end{abstract}
\pagebreak

\tableofcontents
\pagebreak

\section{Introduction}\label{sect:introduction}
Your introduction goes here.

\section{Literature Review}\label{sect:literature_review}
Your literature review goes here.
Just adding~\parencite{Lagasio2024} and~\parencite{Wu2020} for visibility here.
\parencite{Bingler2022}
\parencite{Bingler2024}
\parencite{Callaway2024}
\parencite{Gourier2024}
\parencite{Ilhan2023}


\section{Data}\label{sect:data}

The data collected for the thesis comes from multiple sources. The ESG reports were scraped from the \href{https://responsibilityreports.com}{ResponsibilityReports.com}. The company characteristics, their stock price returns as well as their quarterly earnings have been extracted from the Refinitiv database. Furthermore, a measure of abnormal returns and a greenwashing indicator were constructed.

\subsection{Scraping}

Scraping the ResponsibilityReports.com allowed us to collect company reports relating to ESG and/or CSR. Additionally, it also allowed us to retrieve information on company headquarters location and the approximate number of employees. Table \ref{tab:sust_reps} displays the number of reports per year.

\begin{wrapfigure}{l}{0.5\textwidth}
    \caption{Number of reports per year}\label{tab:sust_reps}
    \begin{tabular}{cc}
        \toprule
        YEAR & Number of Reports\\
        \midrule
        2023 & 1859\\
        2022 & 2020\\
        2021 & 1733\\
        2020 & 1355\\
        2019 & 1081\\
        2018 & 852\\
        2017 & 686\\
        2016 & 558\\
        2015 & 475\\
        2014 & 415\\
        2013 & 357\\
        2012 & 300\\
        2011 & 252\\
        2010 & 216\\
        \bottomrule
    \end{tabular}
\end{wrapfigure}

More text follows here. Generally the next step is to describe what the sustainability reports contain and why are they useful, why I haven't chosen them instead of something else, how they relate to my outcome variables. 
\subsection{Refinitiv}

Here go over the data characteristics, what data you got.

\subsection{Merging}
I will certainly need to reduce these sections to paragraphs but here you should describe the process of merging the data and what observations you lost 
\subsection{Abnormal Returns}

Here talk about making the indicator, how you made it, which market model you used, which indices you used etc. 
\subsection{Greenwashing Indicator}
Talk the reader through the whole methodology of constructing the greenwashing indicator

% \pagebreak

\begin{sidewaystable}
\caption{Sample Composition}
\footnotesize{} % Reduce font size
\setlength{\tabcolsep}{3pt} % Reduce column spacing
\begin{tabular}{lccc|lccc|lccc}
    \toprule
    \multicolumn{4}{c|}{\textbf{ICB Industry}} & \multicolumn{4}{c|}{\textbf{Number of Employees}} & \multicolumn{4}{c}{\textbf{Country of Domicile}} \\
    \cmidrule(lr){1-4} \cmidrule(lr){5-8} \cmidrule(lr){9-12}
    Industry & Total & Treated & Control & Employees & Total & Treated & Control & Country & Total & Treated & Control \\
    \midrule
    Industrials & 120 (19\%) & 59 (18\%) & 61 (19\%) & 10,000+ & 487 (62\%) & 250 (63\%) & 237 (61\%) & United States & 376 (59\%) & 164 (51\%) & 212 (66\%) \\
    Consumer Discretionary & 99 (15\%) & 30 (9.4\%) & 69 (21\%) & 1001--5000 & 134 (17\%) & 70 (18\%) & 64 (16\%) & United Kingdom & 64 (10\%) & 38 (12\%) & 26 (8.1\%) \\
    Financials & 87 (14\%) & 65 (20\%) & 22 (6.9\%) & 5001--10,000 & 120 (15\%) & 54 (14\%) & 66 (17\%) & Canada & 55 (8.6\%) & 30 (9.4\%) & 25 (7.8\%) \\
    Basic Materials & 83 (13\%) & 47 (15\%) & 36 (11\%) & 201--500 & 20 (2.5\%) & 10 (2.5\%) & 10 (2.6\%) & Australia & 48 (7.5\%) & 31 (9.7\%) & 17 (5.3\%) \\
    Consumer Staples & 57 (8.9\%) & 20 (6.3\%) & 37 (12\%) & 501--1000 & 13 (1.6\%) & 5 (1.3\%) & 8 (2.1\%) & Other & 97 (15\%) & 56 (17\%) & 41 (12\%) \\
    Technology & 52 (8.1\%) & 36 (11\%) & 16 (5.0\%) & 11--50 & 8 (1.0\%) & 5 (1.3\%) & 3 (0.8\%) & Unknown & 155 & 84 & 71 \\
    Utilities & 47 (7.3\%) & 10 (3.1\%) & 37 (12\%) & 51--200 & 6 (0.8\%) & 4 (1.0\%) & 2 (0.5\%) & & & & \\
    Health Care & 46 (7.2\%) & 28 (8.8\%) & 18 (5.6\%) & 1--10 & 1 (0.1\%) & 1 (0.3\%) & 0 (0\%) & & & & \\
    Telecommunications & 20 (3.1\%) & 14 (4.4\%) & 6 (1.9\%) & Unknown & 6 & 4 & 2 & & & & \\
    Energy & 17 (2.7\%) & 7 (2.2\%) & 10 (3.1\%) & & & & & & & & \\
    Real Estate & 12 (1.9\%) & 3 (0.9\%) & 9 (2.8\%) & & & & & & & & \\
    Unknown & 155 & 84 & 71 & & & & & & & & \\
    \midrule
    Total & N = 795 & N = 403 & N = 392 & Total & N = 795 & N = 403 & N = 392 & Total & N = 795 & N = 403 & N = 392 \\
    \bottomrule
\end{tabular}\label{tab:sample_composition}
\end{sidewaystable}

% \pagebreak

\section{Methodology}\label{sect:methodology}
Your methodology goes here.

\section{Results}\label{sect:results}
Your results go here.

\section{Discussion}\label{sect:discussion}
Your discussion goes here.

\section{Conclusion}\label{sect:conclusion}
Your conclusion goes here.

\pagebreak
\printbibliography{}
\pagebreak
\appendix

\section{Data}
Your appendix goes here.

\section{Models}
Here's another appendix
\end{document}